Turbulence in compact to giant HII regions

### 2022-01-13 Corr.tex
Javier changes 2022-01-13

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:Reg}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &   0.684$\pm$0.068 &   -0.83$\pm$0.123 &   0.983 &    0.0 \\
 log $\sigma$ &            log L(H) &   0.175$\pm$0.095 &  -6.039$\pm$3.673 &   0.716 &   0.02 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.813$\pm$0.475 &  -0.208$\pm$0.543 &   0.668 &  0.035 \\
      log $m$ &            log Dist &  -0.111$\pm$0.081 &   1.209$\pm$0.155 &  -0.592 &  0.072 \\
 log $\sigma$ &         log $r_{0}$ &   0.221$\pm$0.182 &    0.65$\pm$0.122 &   0.545 &  0.103 \\
      log $m$ &        log $\sigma$ &  -0.142$\pm$0.237 &    0.106$\pm$0.18 &  -0.421 &  0.226 \\
      log $m$ &         log $r_{0}$ &  -0.046$\pm$0.084 &   0.015$\pm$0.055 &  -0.387 &  0.269 \\
\hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &   0.69 $\pm$ 0.07 &   -0.83 $\pm$ 0.12 &   0.98 &    < 10\(^{-4}\) \\
 log $\sigma$ &            log L(H) &   0.25 $\pm$ 0.10 &  -8.90 $\pm$ 3.63 &   0.83 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.78 $\pm$ 0.46 &  -0.17 $\pm$ 0.54 &   0.66 &  0.036 \\
      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &    1.21 $\pm$ 0.16 &  -0.59 &  0.072 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.19 &   0.65 $\pm$ 0.12 &   0.54 &  0.103 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &    0.11 $\pm$ 0.18 &   -0.42 &  0.227 \\
      log $m$ &         log $r_{0}$ &   -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.38 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2022-01-13 strucfunc_paper.tex
Javier changes 2022-01-13

Previous investigations of the centroid velocity structure function in \hii{} regions
have used a variety of methodologies, which makes it difficult to compare results
between different regions.  \citet{arthur2016turbulence} summarise historical results
for the Orion Nebula in their Table~5.
The most significant differences are seen when different emission line tracers are used,
but even when using the same line, there is some variance between different studies
in the derived values for both the velocity dispersion \(\sigma\pos\) and power-law slope \(m\).
It is therefore worthwhile to employ a uniform approach across a variety of different regions.
To that end, we have selected 9 \hii{} regions,
covering a broad range in size and luminosity,
for which good quality mapping of the \ha{} line exists in the literature
or in data archives.
Figure~\ref{fig:hii-regions} shows optical images of
each region in our sample
and Table~\ref{tab:Reg} lists their most important physical parameters.
The derived centroid \ha{} velocity maps are shown in Figure~\ref{fig:velocity-maps}.
Our sample includes three Milky Way regions
(at approximate distance of \num{0.5} to \SI{2}{kpc}),
two regions in the Magellanic Clouds (\num{50} to \SI{60}{kpc}),
and four regions in more distant galaxies of the Local Group
(\num{500} to \SI{800}{kpc}).
Further details of the observations and the sources themselves
are given in the following two sections.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
\bottomrule
\end{tabular}\label{tab:Reg}
\end{center}
\end{table}

@@

The Orion Nebula (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:
%
\begin{equation}\label{eq:Br}
  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
  \,
  \sum_{\text{pairs}} \bigl[
  V_{c}(\xx + \boldsymbol{r}) - V_{c}(\xx)
  \bigr]^{2}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
In the Kolmogorov model \(B(r) \propto r^{2/3}\).

The variance of the centroid velocity fluctuations is:
%
\begin{equation}\label{eq:variance}
\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\xx) -\langle V_ c\rangle  \bigr]^2
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity
%
\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\xx)
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

The autocovariance function is:

\begin{equation}\label{eq:Cr}
C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
\end{equation}
%
and is another statistical tool used in studying the turbulent flows.
The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.

For the homogeneous random field, Equations \ref{eq:Br} and \ref{eq:Cr} are related by:

\begin{equation}\label{eq:functional}
b(r; r_0, \sigma^2, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

%Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
%
%\begin{equation}\label{eq:ff}
%b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
%\end{equation}
%
%where  is now the new form of the correlation function in the form:
where $C(r)$ is a new form that we propose of the correlation function:
%
\begin{equation}\label{eq:ffnew}
  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
\end{equation}
%
substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.

The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:Br} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.

The model proposed to describe the seeing at small scales is:
%
\begin{equation}\label{eq:ffs}
  S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  }
\end{equation}
%
and the model that consider the effect of the observational box size is:

\begin{equation}\label{eq:ffb}
% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
  \beta(r_0) = 1 - \exp \left[ -L_{\text{box}} / (3.6 r_0) \right] 
\end{equation}
%
where $L_{\text{box}}$ is the diagonal length of the observational box.

The final form of our proposed functional of the structure function is in the form:
%
\begin{equation}\label{eq:fff}
B(r) = b(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
\end{equation}

The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares
fit to obtain the best values for the turbulent parameters. 
We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
\end{equation}
%
using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.

In this way we avoid one fundamental problem in the interpretation of the structure function results. 
The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.

@@

\begin{equation}\label{eq:kolm}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}
%
where \(\epsilon\) is the energy transfer rate and the value of $\beta = -5 / 3$ is the Kolmogorov index.
%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.

@@

The true variance of the velocity fields obtained with the analysis in Section \ref{sec:apply} is shown in the second column in Table \ref{tab:Res}. 
For all regions except for Carina and Lagoon there is an slight increase in the value of $\sigma$.

@@

It has been proposed for comparison between two-dimensional observations and the three-dimensional value of the astronomical object what it is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, where:

@@

We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.

@@

Relationship between the physical properties of HII regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}

\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p < $0.05.
In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.

The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region. The relationship we found is relation of $\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)$.

The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.17 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(6 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 2) \log \sigma -(36.23 \pm 1.45)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

>>>>

Previous investigations of the centroid velocity structure function in \hii{} regions
have used a variety of methodologies, which makes it difficult to compare results
between different regions.  \citet{arthur2016turbulence} summarise historical results
for the Orion Nebula in their Table~5.
The most significant differences are seen when different emission line tracers are used,
but even when using the same line, there is some variance between different studies
in the derived values for both the velocity dispersion \(\sigma\pos\) and power-law slope \(m\).
It is therefore worthwhile to employ a uniform approach across a variety of different regions.
To that end, we have selected 9 \hii{} regions,
covering a broad range in size and luminosity,
for which good quality mapping of the \ha{} line exists in the literature
or in data archives.
Figure~\ref{fig:hii-regions} shows optical images of
each region in our sample
and Table~\ref{tab:regions-properties} lists their most important physical parameters.
The derived centroid \ha{} velocity maps are shown in Figure~\ref{fig:velocity-maps}.
Our sample includes three Milky Way regions
(at approximate distance of \num{0.5} to \SI{2}{kpc}),
two regions in the Magellanic Clouds (\num{50} to \SI{60}{kpc}),
and four regions in more distant galaxies of the Local Group
(\num{500} to \SI{800}{kpc}).
Further details of the observations and the sources themselves
are given in the following two sections.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The Orion Nebula (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:
%
\begin{equation}\label{eq:Br}
  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
  \,
  \sum_{\text{pairs}} \bigl[
  V_{c}(\xx + \boldsymbol{r}) - V_{c}(\xx)
  \bigr]^{2}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
The variance of the centroid velocity fluctuations is:
%
\begin{equation}\label{eq:variance}
\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\xx) -\langle V_ c\rangle  \bigr]^2
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity
%
\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\xx)
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

The autocovariance function:

\begin{equation}\label{eq:Cr}
C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
\end{equation}
%
is another statistical tool used in studying the turbulent flows.
The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.

For an homogeneous random field equations \ref{eq:Br} and \ref{eq:Cr} are related by:

\begin{equation}\label{eq:functional}
B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

We use a new functional for the structure function based on equation \ref{eq:functional}. 
First we propose a new \(C(r)\) in the form:
%
\begin{equation}\label{eq:ffnew}
  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
\end{equation}
%
The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
\citet{1984ApJ...277..556S}.

We also take into account in the new functional observational constraints like the seeing and observational box size (see Appendix~\ref{sec:degr-struct-funct} for details).

The seeing becomes important at small scales and it is known that has an effect giving a more pronounced stepping in the structure function.
The model proposed to describe the seeing at small scales is:
%
\begin{equation}\label{eq:ffs}
  S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  }
\end{equation}

The model that consider the effect of the observational box size is:

\begin{equation}\label{eq:ffb}
% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
  \beta(L_{\text{box}},r_0) = 1 - \exp \left[ \frac{-L_{\text{box}}} {3.6 r_0} \right] 
\end{equation}
%
where the \(L_{\text{box}}\) value is the diagonal length of the observational box.

Considering the previous models we obtain the final form of our proposed structure function functional:
%
\begin{equation}\label{eq:proposed-functional}
B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
\end{equation}
%
where the term \( B_{\text{noise}}\) is a correction factor that considers the instrument noise at small scales.
This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated property.

To maintain an uniform methodology across all the sample of HII regions the results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit to obtain the best fit for the analysis. 
For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:proposed-functional} are use in a chi-square analysis following:
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
\end{equation}
%

In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.

@@

\begin{equation}\label{eq:kolm}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}
%
where \(\epsilon\) is the energy transfer rate and the value of $\beta = -5 / 3$ is the Kolmogorov index.
%For supersonic turbulence the index is $\beta=-2$ \citep{burg}. 
%In the Kolmogorov model \(B(r) \propto r^{2/3}\).

@@

%Note to me: review bibliography and expand this section
The true variance of the velocity fields obtained with the analysis in Section \ref{sec:apply} is shown in the second column in Table \ref{tab:Res}. 
For all regions except for Carina and Lagoon there is an slight increase in the value of $\sigma$.

@@

For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed.
This procedure is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.

@@

We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.

@@

%Intro for scaling relations
Relationship between the physical properties of HII regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}

%Previous research on scaling relations
\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

%methods for our analysis
We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p < $0.05.
In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.

%Size vs correlation length
\textit{Note: Regarding the values and uncertainties of the size of the regions, table \ref{tab:regions-properties},  I was fearing that they might seem kind of arbitrary for the reviewers. So I had the idea of using the box size value instead of the size, and the box size minus the maximun separation r for the uncertainty for the regression analysis (not shown). The results are quite consistent with the size, R, value (see lines below) giving $\log r_0 = (0.77 \pm 0.12) \log box size-(0.80 \pm 0.18)$. There is a diminution for the Pearson correlation value from 0.98 to 0.95 and the p-value changes from 3.7e-07 to 4.49e-05.}
The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region. The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).

\textit{Note: First I was using the luminosities values from the table of the Git page for the regression analysis. But I change them according to the bibliography when writing section 2. The values are quite consistent but for Carina there was some difference. From \SI{e39}{erg.s^{-1}} to \SI{e38}{erg.s^{-1}}.}
The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)
